\textbf{Providing Access Control and Copy-on-Write for Content Distribution Network Assets}

### 2016-04-06 tex/paper.tex
Added description of model elements

\subsection{Approach}
As this work only presents an informal model of how the system is designed it can not be regarded as
a proof for the actual implementation of the system to be flawless. The model should however give a 
strong idea of the soundness of the design of the system.

The Copy-on-Write system is only used for files as all of the other objects in the system is
basically just metadata and not classed as important as the actual files themselves, from a data
integrity point of view.

@@

\subsection{Access rights}
The \textit{A[u,c]} notation is symbolising an access token, and if \textit{A[u,c]} exists in
the access matrix \textit{A}, user \textit{u} has full access to the container object \textit{c} and
its children.

@@

@@

%\begin{equation} \label{eq:copy}
%    \begin{split}
%        & f' = f \in m \\
%        & m' = u, copy(m) \Implies \\
%        & m' \neq m \land \\
%        & f' \in m' \land f' \in m
%    \end{split}
%\end{equation}
\vspace{2em}
\textbf{Copy}
\begin{equation} \label{eq:copy}
    \inferrule
    {m \in M \\ c \in C \\ m \in c \\ A[u,c] \in A}
    {M \cup \{m\} \xrightarrow{u, copy(m')} M \cup \{m, m'\} \land m.id \neq m'}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Delete}
\begin{equation} \label{eq:delete}
    \inferrule
    {m \in M \\ f \in F \\ f \in m \\ c \in C \\ m \in c \\ A[u,c] \in A}
    {M \cup \{m\} \land F \cup \{f\} \xrightarrow{u, delete(m)} M \cup \{\} \land F \cup \{f\}}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Snapshot}
\begin{equation} \label{eq:snapshot}
    \begin{split}
        [C', M'] = u, snapshot(tree) \Implies \\
        \forall c \in tree, u, copy(c) \in C \land \\
        \forall m \in tree, u, copy(m) \in M \land \\
        (\forall f \in tree \Implies f \in F)
    \end{split}
\end{equation}

@@

\vspace{2em}
\begin{equation} \label{eq:snapshot2}
    \inferrule
    {c \in C \\ A[u,c] \in A}
    {M \land C \xrightarrow{[C', M'] = u, snapshot(c)} M \cup M' \land C \cup C'}
\end{equation}
If a user creates a snapshot of a container and the full container tree is re-created with new IDs,
but its content still refers to the same files.

>>>>

\subsection{Approach}
As this work only presents an informal model of how the system is designed, it can not be regarded as
a proof for the actual implementation of the system to be flawless. The model should however give a 
strong idea of the soundness of the design of the system.

The Copy-on-Write principle is only used for files as all of the other objects in the system is
basically just metadata and not classed as important as the actual files themselves, from a data
integrity point of view.

@@

\begin{description}
\item[Container] \hfill \\
    A container is what would normally be called a folder in popular speech and in the terms of
    filesystems. A container can contain content objects and more containers, this recursive
    definition results in containers representing a virtual tree structure.

\item[File] \hfill \\
    A file is an actual file, in the same sense as in a file system. A file could be for example a
    video or image.

\item[Content] \hfill \\
    A content object contains a pointer to a file and metadata about that file. The pointer to the
    file within the object can change to a different file, but the content object still keeps the
    same metadata as before.

\item[User] \hfill \\
    A user is a registered user in the system.

\item[Access Matrix] \hfill \\
    The access matrix contains what containers that all the users in the system have access to. If
    A[u,c] exists in the access matrix, user \textit{u} has access to container \textit{c}.

\subsection{Access rights}
Access is only handled on containers and if a user has access to a container it also has access to
all of that containers children.
The \textit{A[u,c]} notation is symbolising an access token, and if \textit{A[u,c]} exists in
the access matrix \textit{A}, user \textit{u} has full access to the container object \textit{c} and
its children.

@@

If the user is irrelevant for the rule described, it is left out from the action, for example u,
read(o) = read(o).

@@

%\begin{equation} \label{eq:copy}
%    \begin{split}
%        & f' = f \in m \\
%        & m' = u, copy(m) \Implies \\
%        & m' \neq m \land \\
%        & f' \in m' \land f' \in m
%    \end{split}
%\end{equation}
\vspace{2em}
\textbf{Copy}
\begin{equation} \label{eq:copy}
    \inferrule
    {m \in M \\ c \in C \\ m \in c \\ A[u,c] \in A}
    {M \cup \{m\} \xrightarrow{u, copy(m')} M \cup \{m, m'\} \land m.id \neq m'.id}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Content Deletion}
\begin{equation} \label{eq:delete}
    \inferrule
    {m \in M \\ f \in F \\ f \in m \\ c \in C \\ m \in c \\ A[u,c] \in A}
    {M \cup \{m\} \land F \cup \{f\} \xrightarrow{u, delete(m)} M \cup \{\} \land F \cup \{f\}}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Snapshot}
\begin{equation} \label{eq:snapshot}
    \begin{split}
        [C', M'] := snapshot(tree) & \Implies \\
        \forall c \in tree, copy(c) \in & C' \\
        \forall m \in tree, copy(m) \in & M' \\
        \forall f \in tree, f \in & F
    \end{split}
\end{equation}

@@

\vspace{2em}
\begin{equation} \label{eq:snapshot2}
    \inferrule
    {c \in C \\ A[u,c] \in A}
    {M, C \xrightarrow{[C', M'] := u, snapshot(c)} M \cup M',  C \cup C'}
\end{equation}
If a user creates a snapshot of a container and the full container tree is re-created with new IDs,
but its content still refers to the same files.
